Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-01 tese/intro.tex
fixed some layout issues

 	Although still nothing replace the physical contact with a person while we communicate, we are at a time where we can do more than just a visual and verbal communication.

@@

@@

	As communications technologies appeared, we adapted the way we communicate. This project aims to re-create how we communicate and make it a process more natural and easy to learn.

@@

	Section \ref{signaling} addresses the signaling component which is not defined on \ac{WebRTC} specifications. The fourth subsection presents the evolution of multimedia content until the hypermedia, its capabilities, synchronization mechanisms and interactivity.

>>>>

@@

	As Martin Geddes\cite{geddes} states, \say{No computer in our lifetimes will ever rival a human voice’s capacity to conveying rich and complex social and emotional meaning} , although nothing replace the physical contact with a person while we communicate, we are at a time when we can do more than just a visual and verbal communication, hypermedia can be added to video and voice in order to extend its value. The concept of structured voice and video synchronized with hypermedia is called hypervoice.

@@

	As communications technologies appeared, we adapted the way we communicate. This project don't aims to replace our video and audio communications, but to enrich them with hyper-media content and make them a more natural and easy to learn process.

@@

	Section \ref{signaling} addresses the signaling component of chat applications, which is not defined on \ac{WebRTC} specifications.

	Section \ref{hypermedia} presents the evolution of multimedia content until the hypermedia, its capabilities, synchronization mechanisms and interactivity.

### 2015-06-01 tese/state02.tex
[ADD] modules, changed titles
fixed some layout issues

\subsection{Signaling, meet and get to know}

@@

  The WebSocket protocol \cite{rfc6455} provides bidirectional communications over a full-duplex socket channel. WebSocket handshake phase specifies an \ac{HTTP} header in order to upgrade to \emph{WebSocket} type of communication, the remainder messages are done without \ac{HTTP} headers, which leads to much smaller messages and better network usage. WebSockets may not be available on every web browser, frameworks like \emph{socket.io}\footnote{\url{http://socket.io/}} and \emph{SockJS}\footnote{\url{http://github.com/sockjs}} uses \ac{HTTP} when there is no support for WebSockets.

@@

  Amongst multiple XMPP server solutions are: \emph{ejabberd}\footnote{\url{http://jabberd.im/}}, \emph{Metronome}\footnote{\url{http://lightwitch.org/metronome}}, \emph{Openfire}\footnote{\url{http://igniterealtime.org/projects/openfire/}} and \emph{Prosody}\footnote{\url{http://prosody.im/}}. \emph{Ejabberd} is the one that implements more \ac{RFC} specifications and \ac{XEP}s\footnote{\url{http://en.wikipedia.org/wiki/Comparison_of_XMPP_server_software}}.

  A more interesting approach for signaling would be \ac{SigOfly}\cite{sigofly} which allows inter-domain real-time communications. \ac{SigOfly} achieves inter-domain communication by making use of the \emph{Identity Providers} of each peer.

>>>>

\subsection{Signaling, meet and get to know}\label{signaling}

@@

  The WebSocket protocol \cite{rfc6455} allows bidirectional communications over a full-duplex socket channel. WebSocket handshake phase specifies an \ac{HTTP} header in order to upgrade to \emph{WebSocket} type of communication, the remainder messages are done without \ac{HTTP} headers, which leads to much smaller messages and better network usage. WebSockets may not be available on every web browser, frameworks like \emph{socket.io}\footnote{\url{http://socket.io/}} and \emph{SockJS}\footnote{\url{http://github.com/sockjs}} uses \ac{HTTP} when there is no support for WebSockets.

@@

  Today, multiple XMPP server implementations exists, such as: \emph{ejabberd}\footnote{\url{http://jabberd.im/}}, \emph{Metronome}\footnote{\url{http://lightwitch.org/metronome}}, \emph{Openfire}\footnote{\url{http://igniterealtime.org/projects/openfire/}} and \emph{Prosody}\footnote{\url{http://prosody.im/}}. \emph{Ejabberd} is the server that implements more \ac{RFC} specifications and \ac{XEP}s\footnote{\url{http://en.wikipedia.org/wiki/Comparison_of_XMPP_server_software}}.

  Another interesting approach for signaling would be \ac{SigOfly} \cite{sigofly} which allows inter-domain real-time communications. \ac{SigOfly} provides inter-domain communication by making use of the \emph{Identity Providers} of each peer.

### 2015-06-01 tese/state04.tex
[ADD] modules, changed titles
fixed some layout issues

\subsection{Extending collaboration tools with time manipulation}

@@

	Streaming protocols like \ac {RTP} were designed for continuous and non-interactive media types, such as audio and video. Discrete and non-interactive media don't need to be streamed through \ac{RTP} because they don't change with. For example, if an image appears in a specific time interval, just the \ac{HTML} or \emph{JavaScript} that will reference the image must be streamed, the image itself is then transferred through \ac{HTTP}.

@@

  {\color{fade}[Model View Controller (Suited for interactive RTP)]}

	With such an interactive \ac{RTP} recorder it is then possible to record, play, fast forward, fast rewind, stop and jump to random positions.

  \cite{interactive_stream} proposed an \ac{RTP} profile for real-time transmission of interactive media. This new profile reuses much of video and audio profile implementation, integrating the interactive component.   \cite{interactive_record} explained how to record interactive video with this new profile.

>>>>

\subsection{Extending collaboration tools with time manipulation}\label{collab}

@@

	Streaming protocols like \ac {RTP} and \ac{RTSP} were designed for continuous and non-interactive media types, such as audio and video. Discrete and non-interactive media don't need to be streamed through \ac{RTP} because they don't change with. For example, if an image appears in a specific time interval, just the \ac{HTML} or \emph{JavaScript} that will reference the image must be streamed, the image itself is then transferred through \ac{HTTP}.

@@

	\cite{interactive_stream} concluded that the ability to extract the objects state in order to synchronize them and the ability intercept events in order to control remote objects, are realized using the \ac{MVC} concept. This concept separates three components within an application. The \emph{Model} represents the information itself. The \emph{View} component shows the \emph{Model} to the user in a suitable and interactive way. The \emph{Controller} represents an action from the user to the \emph {Model}.

	Using \ac{MVC} concept will make possible to implement an interactive \ac{RTP} application that records, play, fast forward, fast rewind, stop and jump to random positions.

  \cite{interactive_stream} also proposed an \ac{RTP} profile for real-time transmission of interactive media. This new profile reuses much of video and audio profile implementation, integrating the interactive component. \cite{interactive_record} explained how to record interactive video with this new profile.
